---
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment = "", warning = FALSE, error = FALSE, message = FALSE)
```

# CRAN Task Views

-   [Official CRAN Task Views](https://cran.r-project.org/web/views/)
-   [Shiny Application](https://jimbrigapps.shinyapps.io/task-views-app/)
-   [Documentation](https://cran-task-views.jimbrig.com)

## Task Views

⭐ = Favorite / Recommendation 

-   [Package Development](../package-development/) ⭐⭐
-   [Webservices](../webservices/) ⭐⭐
-   [Finance](../finance/)
-   [Mapping Tools](../maptools/) ⭐
-   [High Performance Computing](../hpc/)
-   [Taxonomy](../taxonomy/)
-   [Databases](../databases/) ⭐
-   [Model Deployment](../model-deployment/)
-   [Reproducible Research](../reproducible-research/) ⭐
-   [Anamaly Detection](../anamoly-detection/)
-   [Security](../security/)
-   [Time-Series](../timeseries/)
-   [Optimization](../optimization/) ⭐
-   [Graphics](../graphics/)
-   [Numerical Math](../numerical-math/)
-   [Open Data](../opendata/) ⭐
-   [Hydrology](../hydrology/)
-   [Computational environments](../computational-environments/) ⭐⭐

Additionally, I included the `ctv` R package.

## Shiny App

There is also an exploratory [Shiny App](../shiny_app/) that van be viewed at <https://jimbrigapps.shinyapps.io/task-views-app/>

Quickly browse packages and their licenses using a snapshot of task views
retrieved on 2020-02-28.

*Not all packages available on CRAN are shown here, just the ones in CRAN's [Task Views](https://cran.r-project.org/web/views/).*

## Techinical Details and Code

Repo's are added via [git submodules](https://git-scm.com/book/en/v2/Git-Tools-Submodules); 
see the `.gitmodules` file for details.

```{bash, eval=FALSE}
git init

git submodule add git@github.com:ropensci/PackageDevelopment.git package-development
git submodule add git@github.com:ropensci/webservices.git
git submodule add git@github.com:eddelbuettel/ctv-finance.git finance
git submodule add git@github.com:ropensci/maptools.git
git submodule add git@github.com:eddelbuettel/ctv-hpc.git "high-performace-computing"
git submodule add git@github.com:ropensci/taxonomy.git
git submodule add git@github.com:terrytangyuan/ctv-databases.git "databases"
git submodule add git@github.com:terrytangyuan/ctv-model-deployment.git "model-deployments"
git submodule add git@github.com:jdblischak/reproducible-research-ctv.git "reproducible-research"
git submodule add git@github.com:pridiltal/ctv-AnomalyDetection.git "anamoly-detection"
git submodule add git@github.com:hrbrmstr/ctvsecurity.git "security"
git submodule add git@github.com:robjhyndman/ctv-TimeSeries.git "timeseries"
git submodule add git@github.com:hwborchers/ctv-optimization.git "optimization"
git submodule add git@github.com:sctyner/ctv-graphics.git "graphics"
git submodule add git@github.com:cran/ctv.git
git submodule add git@github.com:hwborchers/ctv-numericalmath.git "numerical-math"
git submodule add git@github.com:ropensci/opendata.git opendata
git submodule add git@github.com:ropensci/Hydrology.git hydrology
git submodule add git@github.com:o2r-project/ctv-computational-environments.git computational-environments
git submodule add git@github.com:r-spatial/task_views.git "spacial-and-temporal-spatial"

exit
```

In order to stay up-to-date utilize the `update_submods.sh` shell script:

```{bash, eval=FALSE}
#!/bin/sh

git submodule update --recursive
```

## Remaining CTVs not found on Github:

The remaining task views are taken from CRAN and placed into the [data](data/) folder.

- NOTE: I use pandoc to convert between HTML and Markdown here.

```{r, eval=FALSE, include=TRUE}
remaining <- c(
  "Distributions",
  "Bayesian",
  "Econometrics",
  "Environmetrics",
  "ExperimentalDesign",
  "ExtremeValue",
  "FunctionalData",
  "MachineLearning",
  "MetaAnalysis",
  "Multivariate",
  "NaturalLanguageProcessing",
  "OfficialStatistics",
  "Robust",
  "SocialSciences",
  "Spatial",
  "SpatioTemporal",
  "Survival",
  "WebTechnologies"
)

ctvs <- purrr::map(remaining, function(x) {
  read.ctv(system.file("ctv", paste0(x, ".ctv"), package = "ctv"))
}) %>% setNames(remaining)

purrr::walk2(
  ctvs, 
  names(ctvs), 
  ~ctv::ctv2html(x = .x, file = fs::path("../data/html", paste0(.y, ".html")))
)

fs::dir_create("../data/md")

purrr::walk(basename(fs::dir_ls("../data/html")), function(x) {
  cmd <- paste0("pandoc -o '../data/md/", fs::path_ext_remove(x), ".md' ", x)
  cmd
  system(cmd)
})
```

## Session Info

```{r, results='markup', eval=TRUE, echo=TRUE}
sessioninfo::session_info()
```

## ALL Task Views Detailed Information

To get all CTVs:

```{r, eval=TRUE, results='markup', include=TRUE}
library(ctv)

cdir <- system.file("ctv", package = "ctv")
ctvs <- list.files(cdir, pattern = "\\.ctv$")

rr <- sapply(ctvs,
             function(ctv) {
               cat(sprintf("%25s  ", ctv))
               R <- read.ctv(file.path(cdir, ctv))
               cat("\n")
               R
             },
             simplify = FALSE)
```

and for more details, including the packages within the CTVs:

```{r, results='markup', eval=TRUE}
for (n in names(rr)) {
  cat(n, " :\n", rep.int("=", nchar(n)), "\n", sep = '')
  knitr::knit_print(rr[[n]])
  cat("--------------------------------------------------------\n")
}
```


